---
title: "Analysis"
author: "Filip Dechterenko"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

# Load libraries

```{r libraries and preparation}
set.seed(190425)
library(tidyverse); theme_set(theme_classic(16))
library(lme4)
library(here)

source(here("R","utils.R"))
```

# Load data

Data were preprocesseb by scripts 

```{r load data, warning=FALSE, message=FALSE}

df <- readRDS(here("data", "exp_DRM1", "results_191017.rds"))

df_participants <- readxl::read_excel(here::here("data","exp_DRM1","participants_190509.xlsx"))

plots_dir <- here("plots", "exp_DRM1")

if(!dir.exists(plots_dir)) { dir.create(plots_dir) }

df <- df %>% left_join(df_participants, by = c("subject_id"))

df2 <- readRDS(here("data/exp_DRM1/results_with_tgtdistances_200219.rds"))
```

# Duration of the exp

```{r duration of the exp}
data_pth <- here("data", "exp_DRM1", "results") 

exp_duration <- data_pth %>% 
  dir(pattern = "*.log", full.names = T) %>% 
  purrr::map(read_file) %>% 
  purrr::map_dbl(get_dur) 


```
Average experiment duration: `r (exp_duration / 60) %>% mean() %>% round(2)`, SD = `r (exp_duration / 60) %>% sd() %>% round(2)`

# Desc stat



## Participant data

```{r participant desc}
df_participants %>% summarize(n_total = n(), m_age = mean(age), sd_age = sd(age), n_males = sum(gender == "M"), n_payments = sum(payment == "yes")) %>% knitr::kable(digits=2)
```



```{r desc stat}
df %>% group_by(subject_id, type) %>% 
  summarize(correct = mean(correct)) %>% 
  group_by(type) %>% 
  summarize(m = mean(correct), sd = sd(correct)) %>% 
  knitr::kable(digits = 2)

df %>% group_by(subject_id, type) %>% 
  filter(type != "target") %>% 
  summarize(correct = 1-mean(correct)) %>% 
  group_by(type) %>% 
  summarize(m = mean(correct), sd = sd(correct)) %>% 
  knitr::kable(digits = 2)
```

## New analysis based on review

### Distances from tgt images

```{r}
df2 <- df2 %>% 
  rowwise() %>% 
  mutate(mean_tgt_dist = unlist(dist_to_tgts) %>% mean(),
         min_tgt_dist = unlist(dist_to_tgts) %>% min())
df2 %>% 
  ggplot(aes(x = type, y = mean_tgt_dist)) + 
  stat_summary(fun.data = "mean_cl_boot", size = 1.5) 

df2 %>% 
  ggplot(aes(x = type, y = min_tgt_dist)) + 
  stat_summary(fun.data = "mean_cl_boot", col = "red") + 
  geom_point(alpha = 0.1, position = position_jitter(0.2))

```

## And visualize

```{r results accuracy}

p <- df %>%
  group_by(subject_id, type) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct)) + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = .5) +
  ylab("Perc. correct") +
  geom_violin(trim = F)+
  stat_summary(fun.data = "mean_cl_boot") + 
  xlab("Type") +
  theme(text = element_text(size = 24))
  
p
ggsave(file.path(plots_dir, "Fig_chp4_results_accuracy.svg"), p, width = 6, height = 6)

```

```{r}
df %>% 
  group_by(subject_id, type) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct)) +
  stat_summary(fun.data = "mean_cl_boot") +
  ylim(0,1) + theme(aspect.ratio = 1)



df %>% 
  ggplot(aes(x = type, y = correct)) +
  stat_summary(fun.data = "mean_cl_boot") +
  ylim(0,1) + theme(aspect.ratio = 1) +
  facet_wrap(~subject_id)  

```


## Reaction times

### First remove rt larger than 5~s

```{r}
df_rt <- df %>% filter(rt_key <= 5)

```

### Descriptive statistics

```{r}
df_rt %>%
  group_by(subject_id, type) %>% 
  summarize(rt = mean(rt_key)) %>% 
  group_by(type) %>% 
  summarize(m_rt = mean(rt),sd_rt = sd(rt)) %>% 
  knitr::kable(digits = 2)
```

### Test differences in RT between stimuli

```{r}
lmRT_full <- lmer(log(rt_key) ~ type + (1+type|subject_id), df_rt)
lmRT_null <- lmer(log(rt_key) ~ 1 + (1+type|subject_id), df_rt)

anova(lmRT_full,lmRT_null)

summary(multcomp::glht(lmRT_full, linfct=multcomp::mcp(type="Tukey")))

df_rt %>%
  group_by(subject_id, type) %>% 
  summarize(rt = mean(rt_key)) %>% 
  arrange(subject_id, type) %>% 
  filter(type != "target") %>% 
  lsr::cohensD(rt ~ type, data = ., method = "paired")
```

### Visualize

```{r}
p <- df %>% 
  filter(rt_key < 5) %>% 
  ggplot(aes(x = rt_key)) + 
  theme(aspect.ratio = 1) +
  geom_histogram(binwidth = 0.2) + 
  xlab("RT [s]") + 
  theme(text = element_text(size = 24))
p
ggsave(file.path(plots_dir, "Fig_chp4_results_rt_hist.eps"), p, width = 6, height = 6)

p <- df_rt %>% 
  group_by(subject_id, type) %>% 
  summarize(rt = mean(rt_key)) %>% 
  ggplot(aes(x = type, y = rt)) + 
  theme(aspect.ratio = 1) +
  ylab("RT [s]") +
  geom_violin(trim = F)+
  stat_summary(fun.data = "mean_cl_boot") + 
  xlab("Type") +
  theme(text = element_text(size = 24))
p
ggsave(file.path(plots_dir, "Fig_chp4_results_rt.svg"), p, width = 6, height = 6)
```


## split the analysis for first half and second half. 

```{r}
trial_ids <- df %>% 
  filter(subject_id == 1) %>% 
  pull(trial_id)

cutoff_trial <- trial_ids[round(length(trial_ids)/15/2)*15]

df_acc2 <- df %>% mutate(part = if_else(trial_id<=cutoff_trial, "part1", "part2"))

df_acc2 %>% 
  group_by(type,part) %>% 
  summarize(m = mean(correct), sd = sd(correct)) %>% 
  knitr::kable(digits = 2)

p <- df_acc2 %>% 
  group_by(subject_id, type, part) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct, col = part, group = part)) +
  stat_summary(fun.data = "mean_cl_boot") +
  stat_summary(fun.y = "mean", geom = "line") +
  ylim(0,1) + theme(aspect.ratio = 1) +
  scale_color_discrete("Halves", labels = c("First half", "Second half")) +
  ylab("Perc. correct") + xlab("Type")

p

ggsave(file.path(plots_dir, "Fig_chp4_results_perhalves.svg"), p, width = 6, height = 6)
```


### Running mean for accuracy and rt

```{r}
df_rollmean <- df_acc2 %>% group_by(type) %>% 
  arrange(trial_id) %>% 
  mutate(correct = zoo::rollmean(correct, 250, align = "right", fill = NA), rt = zoo::rollmean(rt_key,250,align = "right", fill = NA))

p <-  df_rollmean %>% 
  ggplot(aes(x = trial_id, y = correct, col = type)) +
  geom_path() + 
  ylim(0,1) + 
  ylab("Perc. correct") + xlab("Trial id") + 
  theme(aspect.ratio = 0.5)

p

ggsave(file.path(plots_dir, "Fig_chp4_results_runningmean.svg"), p, width = 6, height = 6)

p <-  df_rollmean %>% 
  ggplot(aes(x = trial_id, y = rt, col = type)) +
  geom_path() + 
  ylab("Reaction time [s]") + xlab("Trial id") + 
  theme(aspect.ratio = 0.5)

p

ggsave(file.path(plots_dir, "Fig_chp4_results_runningmean_rt.svg"), p, width = 6, height = 6)

```

### Tests

```{r}
df_acc2 %>% group_by(subject_id,type,part) %>% summarize(correct = mean(correct)) %>% filter(type == "target") %>% t.test(correct~part,., paired = T, var.equal = T) %>% apa::apa()
```

## Analysis for first half and second half with respect to payment

```{r analysis payments}
trial_ids <- df %>% 
  filter(subject_id == 1) %>% 
  pull(trial_id)

cutoff_trial <- trial_ids[round(length(trial_ids)/15/2)*15]

df_acc2 <- df %>% mutate(part = if_else(trial_id<=cutoff_trial, "part1", "part2"))

df_acc2 %>% 
  group_by(type,part,payment) %>% 
  summarize(m = mean(correct), sd = sd(correct)) %>% 
  knitr::kable(digits = 2)

df_acc2 %>% 
  group_by(subject_id, type, part, payment) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct, col = part, group = part)) +
  stat_summary(fun.data = "mean_cl_boot") +
  stat_summary(fun.y = "mean", geom = "line") +
  ylim(0,1) + theme(aspect.ratio = 1) +
  facet_grid(~payment)

df_acc2 %>% 
  group_by(subject_id, payment) %>% 
  summarize(correct = mean(correct)) %>% 
  t.test(correct ~ payment, .)
```

```{r payment lmer}

lm1_full <- glmer(correct~type*payment+(1+type|subject_id) + (1|category), df, family = binomial())

lm1_justpayment <- glmer(correct~payment+(1+type|subject_id) + (1|category), df, family = binomial())

lm1_justtype <- glmer(correct~type+(1+type|subject_id) + (1|category), df, family = binomial())

lm1_nointeraction <- glmer(correct~type+payment+(1+type|subject_id) + (1|category), df, family = binomial())

lm1_null <- glmer(correct~1+(1+type|subject_id) + (1|category), df, family = binomial())

anova(lm1_justtype,lm1_null)
av1 <- anova(lm1_justpayment,lm1_null)
av1
av1$Chisq

anova(lm1_justtype,lm1_nointeraction)
anova(lm1_full,lm1_nointeraction)

```

```{r payment part lmer}

lm2_full <- glmer(correct~type*payment*part+(1+type|subject_id) + (1|category), df_acc2, family = binomial())

lm2_justpayment <- glmer(correct~payment+(1+type|subject_id) + (1|category), df_acc2, family = binomial())

lm2_justtype <- glmer(correct~type+(1+type|subject_id) + (1|category), df_acc2, family = binomial())

lm2_justpart <- glmer(correct~part+(1+type|subject_id) + (1|category), df_acc2, family = binomial())

lm2_justpart <- glmer(correct~part+(1+type|subject_id) + (1|category), df_acc2, family = binomial())

lm2_nointeraction <- glmer(correct~type+payment+part +(1+type|subject_id) + (1|category), df_acc2, family = binomial())

lm2_null <- glmer(correct~1+(1+type|subject_id) + (1|category), df_acc2, family = binomial())

anova(lm2_justtype, lm2_null)
av1 <- anova(lm2_justpayment, lm2_null)
av1
av1$Chisq

anova(lm2_justtype, lm2_nointeraction)
anova(lm2_full, lm2_nointeraction)

```

The differences regarding payment is not significant.

# Dprime analysis

```{r two dprimes and bias}
df_dprime2 <- df %>% 
  group_by(subject_id) %>% 
  summarize(H = sum(key_resp == "old" & corrKey == "old")/(sum(corrKey == "old")),
            FA_close = sum(key_resp == "old" & corrKey == "new" & type == "close distractor")/(sum(corrKey == "new" & type == "close distractor")),
            FA_far = sum(key_resp == "old" & corrKey == "new" & type == "far distractor")/(sum(corrKey == "new" & type == "far distractor"))) %>% 
  mutate(d_oldclose = qnorm(H) - qnorm(FA_close),
         d_oldfar = qnorm(H) - qnorm(FA_far),
         c_oldclose = -0.5*(qnorm(H) + qnorm(FA_close)),
         c_oldfar = -0.5*(qnorm(H) + qnorm(FA_far)))
t.test(df_dprime2$d_oldclose, df_dprime2$d_oldfar, paired = T)
t.test(df_dprime2$c_oldclose, df_dprime2$c_oldfar, paired = T)  
colMeans(df_dprime2)

df_dprime2

mean(df_dprime2$d_oldclose) %>% round(2)
mean(df_dprime2$d_oldfar) %>% round(2)
sd(df_dprime2$d_oldclose) %>% round(2)
sd(df_dprime2$d_oldfar) %>% round(2)

mean(df_dprime2$c_oldclose) %>% round(2)
mean(df_dprime2$c_oldfar) %>% round(2)
sd(df_dprime2$c_oldclose) %>% round(2)
sd(df_dprime2$c_oldfar) %>% round(2)
```

```{r use rating to compute ROC}

df_oldclose <- create_roc_data(df, without_type = "far distractor")

df_oldfar <- create_roc_data(df, without_type = "close distractor")

df_oldclose_agg <- df_oldclose %>% group_by(var) %>% summarize(Hs = mean(Hs), FAs = mean(FAs), dprime = mean(dprime))

df_oldfar_agg <- df_oldfar %>% group_by(var) %>% summarize(Hs = mean(Hs), FAs = mean(FAs), dprime = mean(dprime))


p1 <- df_oldclose %>% ggplot(aes(x = FAs, y = Hs, group = as.factor(subject_id))) + 
  geom_path(alpha = I(0.2)) + 
  xlim(0,1) + 
  ylim(0,1) + 
  geom_segment(x = 0, y = 0, xend = 1,yend = 1) +
  theme(aspect.ratio = 1) +
  geom_path(data = df_oldclose_agg, group = 1, size = 1.5, col = "red") + 
  ggtitle("Target - Close distractor") +
  theme(text = element_text(size = 24))

p2 <- df_oldfar %>% ggplot(aes(x = FAs, y = Hs, group = as.factor(subject_id))) + 
  geom_path(alpha = I(0.2)) + 
  xlim(0,1) + 
  ylim(0,1) + 
  geom_segment(x = 0, y = 0, xend = 1,yend = 1) +
  theme(aspect.ratio = 1) +
  geom_path(data = df_oldfar_agg, group = 1, size = 1.5, col = "red") + 
  ggtitle("Target - Far distractor") +
  theme(text = element_text(size = 24))

# there were problem with transparency, I needed to save it as svg and save manually as eps

ggsave(file.path(plots_dir, "Fig_chp4_results_ROC_oldclose.svg"), p1, width = 6, height = 6)

ggsave(file.path(plots_dir, "Fig_chp4_results_ROC_oldfar.svg"), p2, width = 6, height = 6)

```

```{r slopes ROC}
slope_oldclose <- get_ROC_slopes(df_oldclose)
slope_oldfar <- get_ROC_slopes(df_oldfar)
intercepts_oldclose <- get_ROC_intercepts(df_oldclose)
intercepts_oldfar   <- get_ROC_intercepts(df_oldfar)


df_dprime2_da <- df_dprime2 %>% mutate(s_oldclose = slope_oldclose,
                      s_oldfar = slope_oldfar) %>% 
  mutate(da_oldclose = compute_da(H,FA_close,s_oldclose),
         da_oldfar = compute_da(H,FA_far,s_oldfar))



mean(df_dprime2_da$da_oldclose) %>% round(2)
mean(df_dprime2_da$da_oldfar) %>% round(2)
sd(df_dprime2_da$da_oldclose) %>% round(2)
sd(df_dprime2_da$da_oldfar) %>% round(2)


df_dprime2_da %>% select(da_oldclose,da_oldfar) %>% arrange(da_oldfar)
t.test(df_dprime2_da$da_oldclose, df_dprime2_da$da_oldfar, paired = T) %>% apa::apa()
lsr::cohensD(df_dprime2_da$da_oldclose, df_dprime2_da$da_oldfar,method = "paired")
```

slope
*  old-close: `r mean(slope_oldclose) %>% round(2)`, SD = `r sd(slope_oldclose) %>% round(2)`
*  old-far: `r mean(slope_oldfar) %>% round(2)`, SD = `r sd(slope_oldfar) %>% round(2)`

```{r test nonunit slope}

t.test(slope_oldclose, mu = 1)
t.test(slope_oldfar, mu = 1)
```

```{r SDT model plot}
df_dprime <- df %>% group_by(subject_id,type) %>% 
  
  summarize(yes = mean(key_resp == "old"),
            zH = qnorm(yes)) %>% 
  mutate(d_old_close = zH[type == "target"]-zH[type == "close distractor"],
         d_old_far = zH[type == "target"]-zH[type == "far distractor"],
         d_close_far = zH[type == "close distractor"]-zH[type == "far distractor"])


df_dprime_agg <- df_dprime %>% 
  group_by(type) %>% 
  summarize(m = mean(zH),sd = sd(zH))

df_dprime_agg

x0 <- (-400:400)/100

y_close  <- dnorm(x0, df_dprime_agg$m[df_dprime_agg$type == "close distractor"], mean(slope_oldclose))
y_far  <- dnorm(x0, df_dprime_agg$m[df_dprime_agg$type == "far distractor"], mean(slope_oldfar))
y_target  <- dnorm(x0, df_dprime_agg$m[df_dprime_agg$type == "target"], 1)

df_plot <- tibble(x = rep(x0,3), y = c(y_close, y_far, y_target), type = rep(c("close distractor","far distractor","target"), each = length(x0)))

p_SDT_model <- df_plot %>% ggplot(aes(x = x, y = y, col = type)) + geom_path(size = 1.2) + geom_vline(xintercept = 0) +
  theme(aspect.ratio = 1)
p_SDT_model
ggsave(file.path(plots_dir, "Fig_chp4_results_dprimedistance.svg"), p_SDT_model, width = 6, height = 6)

(df_dprime_agg$m[df_dprime_agg$type == "close distractor"]-df_dprime_agg$m[df_dprime_agg$type == "target"]) %>% round(2)

(df_dprime_agg$m[df_dprime_agg$type == "far distractor"]-df_dprime_agg$m[df_dprime_agg$type == "close distractor"]) %>% round(2)
```



# Per image accuracy

```{r per image accuracy}
df_perimage <- df %>% group_by(img_name,type) %>% summarize(m = mean(correct), sd = sd(correct)) %>% arrange(-m)

order_category <- 
  df %>%
  group_by(category) %>% 
  do(Hmisc::smean.cl.boot(.$correct) %>% t() %>% as_tibble()) %>% 
  arrange(Mean) %>% 
  ungroup() %>% 
  mutate(category = forcats::as_factor(category), rank = 1:n())

p_ordercat <- order_category %>%
  ggplot(aes(x = category, xend = category, y = Lower, yend = Upper, group = 1)) +
  geom_segment(size = 1.2) +
  geom_point(aes(y=Mean), size = 3) + 
  theme(aspect.ratio = 0.2) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 16)) + 
  theme(legend.position = "top") + 
  xlab("Category") + 
  ylab("Accuracy")
  
p_ordercat
ggsave(file.path(plots_dir, "Fig_chp4_results_categories.svg"), p_ordercat, width = 9, height = 6)
```

# Memorability

Memorability were computed using pretrained CNN

```{r load mem data}
mem_imgnames <- read_csv(here("data/exp_DRM1/memorability/memorability_imgnames.txt"), col_names = F)
mem_values <- read_csv(here("data/exp_DRM1/memorability/memorability_all.txt"), col_names = F)

df_mem <- tibble(img_name = mem_imgnames$X1, mem_score = mem_values$X1)
dfm <- df_perimage %>% left_join(df_mem,by = "img_name") %>% rename(correct = m)

(cor.test(~correct+mem_score, dfm %>% filter(type == "target")) %>% papaja::apa_print.htest())$full_result
(cor.test(~correct+mem_score, dfm %>% filter(type == "close distractor")) %>% papaja::apa_print.htest())$full_result
(cor.test(~correct+mem_score, dfm %>% filter(type == "far distractor")) %>% papaja::apa_print.htest())$full_result
```

## Test 

```{r overall glmer}
lm1 <- glmer(correct~type+(1+type|subject_id) + (1|category), df %>% filter(type!="target"), family = binomial())

lmnull <- glmer(correct~1+(1+type|subject_id) + (1|category), df %>% filter(type!="target"), family = binomial())

anova(lm1,lmnull)
```

```{r one sample tests}
df_for_onettest <- df %>% group_by(subject_id,type) %>% summarize(correct = mean(correct))
df_for_onettest %>% group_by(type) %>% do(t.test(.$correct, mu = .5) %>% broom::tidy()) %>% 
  left_join(df_for_onettest %>% group_by(type) %>% do(d=lsr::cohensD(.$correct, mu = .5)) %>% mutate(d = unlist(d)),
            by = "type")


```